Interactive web based flood modeling at country wide scale and planter size resolution.

### 2014-03-07 article.tex
writing

\documentclass[a4paper]{article}
\usepackage{iemss}
\usepackage[pdftex]{graphicx}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage[labelfont=bf,textfont=sf,labelsep=period]{caption}
\usepackage[english]{babel}
%\RequirePackage{lineno} % for line numbers

@@

%Authors Names and Affiliations:  Two spaces below the title, 10 pt
%Arial, Upper and Lower Case, underline author presenting
%paper and  provide his/her email address

@@

The flooding of rural and urban areas is an increasing hazard to society. Accurate and timely predictions are essential for the water manager to be able to carefully plan, design and control the effects of flooding hazard.
For the prediction of these flooding hazards requires a numerical model that represents the physical processes (rain, evaporation, flow, infiltration). This model is fed with measurements from current or historic events. The results of these calculations, the expected flooding, is used for damage estimates, dike design, spatial and emergency planning and for coordinating response efforts.
Several challenges required an innovative redesign of both the numerical model and the information infrastructure where it is nested within.
The traditional working method for modelers is to prepare the input of the schematization (grid and input measurements), run a model, wait a while for the model to complete and finally post-process the results. This is working method is suitable for confirmatory modeling (making the best prediction a few days ahead). Most of the questions that people use numerical models for are exploratory. To effectively plan and design a water system it is important to provide an indication of the effect of a measure in seconds, not over night or even over coffee.

@@

The amount of data involved in preparing the model is rapidly increasing. There is an increase in supply of data caused by the ever growing measurement resolution and spatial coverage. For example the topology of waterbodies at a spatial coverage of a small country are used to determine if the water will find its way into ones neighborhood. The topography and infiltration rate at a spatial resolution of a planter determine if the water will flow to ones backyard or the neighbors.
This resulted in the question how can we design a platform that is suitable for this new modeling approach and meets the corresponding challenges.

@@

\section{Method}

Header of the first page should be as appears in this instructions' paper (right justified). Headers of following pages should be: the name of the authors (initial(s) and name) / title of the paper (centered). If there are more than two authors write first author et al. If the title is too long, cut the title where needed and put three dots. Headers text should be in italics 8 pt. Arial.
No footer should appear. \textbf{Do not} number the pages. Numbering of the pages will be done by the editors of the Proceedings.

\section{Results}
Equations should be numbered consecutively as they appear in the
text with Arabic numerals and should be referred to by their
numbers only, e.g. (3).  Equations must be typed not hand printed.
About 5 mm should be left clear above and below each equation.

\begin{figure}[h]
\centering
\includegraphics[width=10cm]{interpolationlevees2}
\caption{Interpolation method}
\label{fig1}
\end{figure}

@@

It was shown by \citet{berry:teomowcihbsi} that...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{iemss}
\bibliography{iemss}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\documentclass[a4paper]{article}
\usepackage{iemss}
\usepackage[pdftex]{graphicx}
\usepackage[authoryear]{natbib}
\usepackage[labelfont=bf,textfont=sf,labelsep=period]{caption}
\usepackage[english]{babel}
% \RequirePackage{lineno} % for line numbers

@@

% Authors Names and Affiliations:  Two spaces below the title, 10 pt
% Arial, Upper and Lower Case, underline author presenting
% paper and  provide his/her email address

@@

The flooding of rural and urban areas is an increasing hazard to society. Accurate and timely predictions are essential for the water manager to be able to carefully plan, design and control the effects of flooding hazard.
For the prediction of these flooding hazards requires a numerical model that represents the physical processes (rain, evaporation, flow, infiltration). This model is fed with measurements from current or historic events. The results of these calculations, the expected flooding, is used for damage estimates, dike design, spatial and emergency planning and for coordinating response efforts. Several challenges required an innovative redesign of both the numerical model and the information infrastructure where it is nested within.

These challenges arise from the movement towards more efficient working methods.
\begin{itemize}
\item \emph{Confirmatory versus exploratory}  \cite{Baart2013}
\item \emph{Passive versus interactive}
\item \emph{Solitary versus social}
\end{itemize}

Other challenges arise from the increased data volumes.
\begin{itemize}
  \item \emph{Measurements}
  \item \emph{Communication}
\end{itemize}

The traditional working method for modelers is to prepare the input of the schematization (grid and input measurements), run a model, wait a while for the model to complete and finally post-process the results. This is working method is suitable for confirmatory modeling (making the best prediction a few days ahead). Most of the questions that people use numerical models for are exploratory.

@@

The amount of data involved in preparing the model is rapidly increasing. There is an increase in supply of data caused by the ever growing measurement resolution and spatial coverage. For example the topology of waterbodies at a spatial coverage of a small country are used to determine if the water will find its way into ones neighborhood. The topography and infiltration rate at a spatial resolution of a planter determine if the water will flow to ones backyard or the neighbors.
This resulted in the question how can we design a platform that is suitable for this new modeling approach and meets the corresponding challenges.

@@

\section{Method}
\subsection{}
\subsection{}

\section{Results}
\subsection{Numerical model}
\subsection{Architecture}
\subsection{Communication}
\subsection{Visualization}
\begin{figure}[h]
  \centering
  \includegraphics[width=10cm]{interpolationlevees2}
  \caption{Interpolation method}
  \label{fig1}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{iemss}
\bibliography{bibliography}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
